Abstract Data Type Inference

### 2015-03-21 histories.tex
Added history examples.

  TODO HISTORY EXAMPLE

@@

  TODO HISTORY OF AN EXECUTION

>>>>

  We draw histories by writing one operation per line, starting with its
  operation identifier and match target, followed by its method label,
  possibly a read-only marker, and its happens-before interval. For instance,
  in the history
\begin{verbatim}
    [1:1] write(a)        #
    [2:1] read => a (RO)    #
\end{verbatim}
  Operation~$1$ is a write operation which matches itself, and precedes a
  read-only read operation which also targets Operation~$1$. Note that we
  only label method argument and return values for illustrative purposes;
  histories do not keep them. In the following history, Operations~$1$ and~$2$
  execute concurrently
\begin{verbatim}
    [1:1] write(a)        #
    [2:1] read => a (RO)  #
    [3:X] read => b (RO)    #
\end{verbatim}
  and Operation~$3$ has no match.

@@

  The histories of the Executions of Example~\ref{ex:executions} are
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)          #
    [3:1] read => a (RO)      #
\end{verbatim}
  in which all three operations are sequential,
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)        #
    [3:1] read => a (RO)    #
\end{verbatim}
  in which the first two operations overlap, and
\begin{verbatim}
    [1:1] write(a)        #
    [2:2] write(b)          #
    [3:1] read => a (RO)    #
\end{verbatim}
  in which the last two operations overlap.
  TODO SAY SOMETHING INTERESTING IN THIS EXAMPLE
\end{example}
